Identify max rank for AUCell

### 2025-02-03 analyses/cell-type-ewings/exploratory_analysis/07-identify-max-rank-aucell.Rmd
address spelling errors

> It is important to check that most cells have at least the number of expressed/detected genes that are going to be used to calculate the AUC (aucMaxRank in calcAUC()). The histogram provided by AUCell_buildRankings() allows to quickly check this distribution.

@@

    genes_to_remove <- rowData(sce)$detected > 0 
    filtered_sce <- sce[genes_to_remove > 0 , ]

@@

Now we will look at the potential thresholds for `aucMaxRank` using 5% and 1% of genes. 
The numbers printed here represent the total number of genes that would be used as the `aucMaxRank` for a given dataset using the threshold. 
We can then use the histograms to see how many cells have at least that number of genes detected. 
Remember, we want to pick a number of genes that are detected in most cells.
If we picked a max rank higher than the number of genes detected in most cells, the non-detected genes that are randomly ordered would play an outsized role in our AUC values.

>>>>

> It is important to check that most cells have at least the number of expressed/detected genes that are going to be used to calculate the AUC (`aucMaxRank` in `calcAUC`()). The histogram provided by `AUCell_buildRankings`() allows to quickly check this distribution.

@@

    genes_to_remove <- rowData(sce)$detected > 0 
    filtered_sce <- sce[genes_to_remove , ]

@@

Now we will look at the potential thresholds for `aucMaxRank` using 5% and 1% of genes. 
The numbers printed here represent the total number of genes that would be used as the `aucMaxRank` for a given dataset using the threshold. 
We can then use the histograms to see how many cells have at least that number of genes detected. 
Remember, we want to pick a number of genes that are detected in most cells.
If we picked a max rank higher than the number of genes detected in most cells, the non-detected genes that are randomly ordered would play an oversized role in our AUC values.
